---
title: "Explanation"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Explanation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(thecentraldogma)
```

# Packages description

## random_dna

## replacement_of_matches

## seq_to_codons

**Description**

seq_to_codons is a function that takes a nucleotide sequence and splits it into the codons, starting at the position specified.

**Usage**

```         
seq_to_codons(sequence, start = 1)
```

**Arguments**

|            |                                                                                      |
|-------------|-----------------------------------------------------------|
| `sequence` | A nucleotide sequence                                                                |
| `start`    | The first position in the nucleotide sequence that should start the codon splitting. |

The codons of the input sequence is outputted as a vector of strings.

**Examples**

```{r}
seq_to_codons("ACTGATCATGA", start=1)
```

## translate_codons

## plot_count
